Kindly Bent to Free Us

### 2019-05-17 kindly/main.tex
motivational section added
vault
Add typing for pairs and complete the kinds/lattices.
Start working on the examples.
abstract take one

\documentclass[manuscript,author]{acmart}

@@

% Math
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
% \usepackage{mathrsfs}
\usepackage{mathtools}
% \usepackage{textcomp}
% \usepackage{textgreek}

@@

\usepackage{natbib}% Good citations and bibliography
\usepackage{mathpartir} % Syntax trees
\usepackage[nameinlink,capitalize]{cleveref}

@@

\input{prelude}
\input{notations}

@@

\title{Kindly Bent to Free Us}
\begin{abstract}
  System programming often requires to manipulate resources that
  cannot be duplicated such as file system handles, network connections
  or even globally allocated memory.
  Unfortunately such resources are often the root of bugs and security issues
  through use-after-free errors or data races, even in the context
  of programming language traditionally considered safe, such as statically typed
  functional languages.
  Linear and affine type systems propose to forbid such erroneous programming
  patterns by tracking usage of variables through types.

@@

\input{intro}
\input{lang}

>>>>

\documentclass[acmsmall,review,anonymous,table]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

% Math
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
% \usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage{gensymb}
% \usepackage{textgreek}

\usepackage{listings}
\usepackage[scaled=0.85]{DejaVuSansMono}

\usepackage{tikz}
\usetikzlibrary{arrows}

@@

\usepackage{natbib}% Good citations and bibliography
\usepackage{mathpartir} % Syntax trees

\usepackage[nameinlink,capitalize]{cleveref}
\addto\extrasenglish{%
  \def\sectionautorefname{Section}
  \def\subsectionautorefname{Section}
  \def\subsubsectionautorefname{Section}
  \def\lstnumberautorefname{Line}
}

@@

\input{prelude}
\input{caml}
\input{notations}

@@

\title{Kindly Bent to Free Us}
\begin{abstract}
  System programming often requires to manipulate resources that
  cannot be duplicated such as file system handles, network connections,
  or globally allocated memory.
  Improper handling of such resources is often the cause of bugs and security issues
  through use-after-free errors or data races. These problems are not
  prevented by most statically typed programming languages that only
  guarantee type soundness and memory safety.
  Linear and affine type systems support tracking of single-threaded resource usage
  through types, but they are often too restrictive for real-world applications.

@@

\input{intro}
\input{motivation}
\input{lang}
